---
title: "Oceania Region Buoy Report"
author: "Mengyun Li, Sijia Li, Siran Zhao, Jinghan Cui"
date: "2017/11/5"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(lubridate)
library(ggplot2)
library(ggmap)
library(data.table)
library(knitr)
library(ggpubr)
```
We select 5 buoys respectively at the north, south, east, west and middle points from the Oceania region, as labeled on the map. Therefore, we can have an approximate estimation of the vast region. The data are collected approximately through a 20-year period from 1980 to 2017.

```{r, echo = FALSE}
## Map
oceania<- c(-100, -10, -190 , 10)
ggmap(get_map(location = oceania, scale = 1, zoom = 3,source = "google", maptype = "terrain"))+
  geom_point(aes(x=-155,y=0),alpha=0.5,size=3,color="red")+
  geom_point(aes(x=-195,y=8),alpha=0.5,size=3,color="red")+
  geom_point(aes(x=-195,y=-8),alpha=0.5,size=3,color="red")+
  geom_point(aes(x=-110,y=-8),alpha=0.5,size=3,color="red")+
  geom_point(aes(x=-110,y=8),alpha=0.5,size=3,color="red")
```

For each buoy, we collect two kinds of data, one is air temperature and the other is sea surface temperature. All of the temperatures are measured at 12:00pm in local time. The original datasets are stored separately as air temperature and sea surface temperature for each buoy in text format.We import all of the ten datasets into R. As they show in the text file, we treat -9.999 and -9.99 as NAs and remove them and unrelated information, then merge the datasets and reorder the columns. The final data is exported as a csv file with 5 separate tab for each buoy’s data. 

```{r, echo = FALSE}
# Remove unrelated rows
N0W155_air <- read.csv("TAO_T0N155W_M_AIRT_daily.ascii", sep="", header = FALSE)
N0W155_air <- N0W155_air[-c(1,2),-c(2,4:14)]
N0W155_sea <- read.csv("TAO_T0N155W_M_SST_daily.ascii", sep="", header = FALSE)
N0W155_sea <- N0W155_sea[-c(1,2),-c(4:14)]
N0W155_air.tidy <- N0W155_air %>% filter(V1 != "Height",V1!="YYYYMMDD", V1 != "Deployment:")
N0W155_sea.tidy <- N0W155_sea %>% filter(V1 != "Height",V1!="YYYYMMDD", V1 != "Deployment:", V1 != "Depth")
# Rename column names
colnames(N0W155_sea.tidy) <- c("date_time","time_diff","sea_temp")
colnames(N0W155_air.tidy) <- c("date_time","air_temp")
# Join to one data set
N0W155_air.tidy[,1]<-as.character(N0W155_air.tidy[,1])
N0W155_air.tidy[,2]<-as.character(N0W155_air.tidy[,2])
N0W155_sea.tidy[,1] <-as.character(N0W155_sea.tidy[,1])
N0W155_sea.tidy[,2] <-as.character(N0W155_sea.tidy[,2])
N0W155_sea.tidy[,3] <-as.character(N0W155_sea.tidy[,3])

N0W155_temp<-full_join(N0W155_sea.tidy,N0W155_air.tidy, by ="date_time", copy = FALSE)
# Add team_num, reading_type, time_diff, latitude, longtitude
N0W155_temp $team_num <-"14"
N0W155_temp $reading_type <-"buoy"
N0W155_temp $time_diff <-"0"
N0W155_temp $Lat <-"0"
N0W155_temp $Lon <-"-155"
# Reorder the clumns
N0W155_temp<-N0W155_temp[,c('team_num','reading_type','time_diff','date_time','Lat','Lon','sea_temp','air_temp')]

# Add hours to date_time
N0W155_temp$date_time <- ymd(N0W155_temp$date_time)
hour(N0W155_temp$date_time) <- 12

# Change data type
N0W155_temp $team_num <-as.integer(N0W155_temp $team_num)
N0W155_temp $Lat <-as.numeric(N0W155_temp$Lat)
N0W155_temp $Lon <-as.numeric(N0W155_temp$Lon)
N0W155_temp$sea_temp <-as.numeric(N0W155_temp$sea_temp)
N0W155_temp$air_temp <-as.numeric(N0W155_temp$air_temp)
#id<-c(1,2,3,4)
#time<-c("00:00:01","01:02:00","09:30:01","14:15:25")
#df<-data.frame(id,time)
#df$time = as.POSIXct(df$time, format = "%H:%M:%S")
#N0W155_temp$time_diff = as.POSIXct(N0W155_temp$time_diff, format = "%H:%M:%S")
#is.POSIXct(N0W155_temp$time_diff)

# Remove NAs
N0W155_temp$sea_temp[N0W155_temp$sea_temp=="-9.999"]<-NA
N0W155_temp$air_temp[N0W155_temp$air_temp=="-9.99"]<-NA
N0W155_temp<-na.omit(N0W155_temp)
```

```{r, echo = FALSE}
# Remove unrelated rows
N8E165_air <- read.csv("TAO_T8N165E_M_AIRT_daily.ascii", sep="", header = FALSE)
N8E165_air <- N8E165_air[-c(1,2),-c(2,4:14)]
N8E165_sea <- read.csv("TAO_T8N165E_M_SST_daily.ascii", sep="", header = FALSE)
N8E165_sea <- N8E165_sea[-c(1,2),-c(4:14)]
N8E165_air.tidy <- N8E165_air %>% filter(V1 != "Height",V1!="YYYYMMDD", V1 != "Deployment:")
N8E165_sea.tidy <- N8E165_sea %>% filter(V1 != "Height",V1!="YYYYMMDD", V1 != "Deployment:", V1 != "Depth")
# Rename column names
colnames(N8E165_sea.tidy) <- c("date_time","time_diff","sea_temp")
colnames(N8E165_air.tidy) <- c("date_time","air_temp")
# Join to one data set
N8E165_air.tidy[,1]<-as.character(N8E165_air.tidy[,1])
N8E165_air.tidy[,2]<-as.character(N8E165_air.tidy[,2])
N8E165_sea.tidy[,1] <-as.character(N8E165_sea.tidy[,1])
N8E165_sea.tidy[,2] <-as.character(N8E165_sea.tidy[,2])
N8E165_sea.tidy[,3] <-as.character(N8E165_sea.tidy[,3])

N8E165_temp<-full_join(N8E165_sea.tidy,N8E165_air.tidy, by ="date_time", copy = FALSE)
# Add team_num, reading_type, time_diff, latitude, longtitude
N8E165_temp $team_num <-"14"
N8E165_temp $reading_type <-"buoy"
N8E165_temp $time_diff <-"0"
N8E165_temp $Lat <-"8"
N8E165_temp $Lon <-"165"
# Reorder the clumns
N8E165_temp<-N8E165_temp[,c('team_num','reading_type','time_diff','date_time','Lat','Lon','sea_temp','air_temp')]

# Add hours to date_time
N8E165_temp$date_time <- ymd(N8E165_temp$date_time)
hour(N8E165_temp$date_time) <- 12

# Change data type
N8E165_temp $team_num <-as.integer(N8E165_temp $team_num)
N8E165_temp $Lat <-as.numeric(N8E165_temp$Lat)
N8E165_temp $Lon <-as.numeric(N8E165_temp$Lon)
N8E165_temp$sea_temp <-as.numeric(N8E165_temp$sea_temp)
N8E165_temp$air_temp <-as.numeric(N8E165_temp$air_temp)

# Remove NAs
N8E165_temp$sea_temp[N8E165_temp$sea_temp=="-9.999"]<-NA
N8E165_temp$air_temp[N8E165_temp$air_temp=="-9.99"]<-NA
N8E165_temp<-na.omit(N8E165_temp)
```

```{r, echo = FALSE}
# Remove unrelated rows
S8E165_air <- read.csv("TAO_T8S165E_M_AIRT_daily.ascii", sep="", header = FALSE)
S8E165_air <- S8E165_air[-c(1,2),-c(2,4:14)]
S8E165_sea <- read.csv("TAO_T8S165E_M_SST_daily.ascii", sep="", header = FALSE)
S8E165_sea <- S8E165_sea[-c(1,2),-c(4:14)]
S8E165_air.tidy <- S8E165_air %>% filter(V1 != "Height",V1!="YYYYMMDD", V1 != "Deployment:")
S8E165_sea.tidy <- S8E165_sea %>% filter(V1 != "Height",V1!="YYYYMMDD", V1 != "Deployment:", V1 != "Depth")
# Rename column names
colnames(S8E165_sea.tidy) <- c("date_time","time_diff","sea_temp")
colnames(S8E165_air.tidy) <- c("date_time","air_temp")
# Join to one data set
S8E165_air.tidy[,1]<-as.character(S8E165_air.tidy[,1])
S8E165_air.tidy[,2]<-as.character(S8E165_air.tidy[,2])
S8E165_sea.tidy[,1] <-as.character(S8E165_sea.tidy[,1])
S8E165_sea.tidy[,2] <-as.character(S8E165_sea.tidy[,2])
S8E165_sea.tidy[,3] <-as.character(S8E165_sea.tidy[,3])

S8E165_temp<-full_join(S8E165_sea.tidy,S8E165_air.tidy, by ="date_time", copy = FALSE)
# Add team_num, reading_type, time_diff, latitude, longtitude
S8E165_temp $team_num <-"14"
S8E165_temp $reading_type <-"buoy"
S8E165_temp $time_diff <-"0"
S8E165_temp $Lat <-"-8"
S8E165_temp $Lon <-"165"
# Reorder the clumns
S8E165_temp<-S8E165_temp[,c('team_num','reading_type','time_diff','date_time','Lat','Lon','sea_temp','air_temp')]

# Add hours to date_time
S8E165_temp$date_time <- ymd(S8E165_temp$date_time)
hour(S8E165_temp$date_time) <- 12

# Change data type
S8E165_temp $team_num <-as.integer(S8E165_temp $team_num)
S8E165_temp $Lat <-as.numeric(S8E165_temp$Lat)
S8E165_temp $Lon <-as.numeric(S8E165_temp$Lon)
S8E165_temp$sea_temp <-as.numeric(S8E165_temp$sea_temp)
S8E165_temp$air_temp <-as.numeric(S8E165_temp$air_temp)

# Remove NAs
S8E165_temp$sea_temp[S8E165_temp$sea_temp=="-9.999"]<-NA
S8E165_temp$air_temp[S8E165_temp$air_temp=="-9.99"]<-NA
S8E165_temp<-na.omit(S8E165_temp)
```

```{r, echo = FALSE}
# Remove unrelated rows
N8W110_air <- read.csv("TAO_T8N110W_M_AIRT_daily.ascii", sep=" ", header = FALSE)
N8W110_air <- N8W110_air[-c(1,2),-c(2,4:14)]
N8W110_sea <- read.csv("TAO_T8N110W_M_SST_daily.ascii", sep=" ", header = FALSE)
N8W110_sea <- N8W110_sea[-c(1,2),-c(4:14)]
N8W110_air.tidy <- N8W110_air %>% filter(V1 != "Height",V1!="YYYYMMDD", V1!= "Deployment:")
N8W110_sea.tidy <- N8W110_sea %>% filter(V1 != "Height",V1!="YYYYMMDD", V1 != "Deployment:", V1 != "Depth")
# Rename column names
colnames(N8W110_sea.tidy) <- c("date_time","time_diff","sea_temp")
colnames(N8W110_air.tidy) <- c("date_time","air_temp")
# Join to one data set
N8W110_air.tidy[,1]<-as.character(N8W110_air.tidy[,1])
N8W110_air.tidy[,2]<-as.character(N8W110_air.tidy[,2])
N8W110_sea.tidy[,1]<-as.character(N8W110_sea.tidy[,1])
N8W110_sea.tidy[,2]<-as.character(N8W110_sea.tidy[,2])
N8W110_sea.tidy[,3]<-as.character(N8W110_sea.tidy[,3])

N8W110_temp<-full_join(N8W110_sea.tidy,N8W110_air.tidy, by ="date_time", copy = FALSE)
# Add team_num, reading_type, time_diff, latitude, longtitude
N8W110_temp $team_num <-"14"
N8W110_temp $reading_type <-"buoy"
N8W110_temp $time_diff <-"0"
N8W110_temp $Lat <-"8"
N8W110_temp $Lon <-"-110"
# Reorder the clumns
N8W110_temp<-N8W110_temp[,c('team_num','reading_type','time_diff','date_time','Lat','Lon','sea_temp','air_temp')]

# Add hours to date_time
N8W110_temp$date_time <- ymd(N8W110_temp$date_time)
hour(N8W110_temp$date_time) <- 12

# Change data type
N8W110_temp $team_num <-as.integer(N8W110_temp $team_num)
N8W110_temp $Lat <-as.numeric(N8W110_temp$Lat)
N8W110_temp $Lon <-as.numeric(N8W110_temp$Lon)
N8W110_temp$sea_temp <-as.numeric(N8W110_temp$sea_temp)
N8W110_temp$air_temp <-as.numeric(N8W110_temp$air_temp)

# Remove NAs
N8W110_temp$sea_temp[N8W110_temp$sea_temp=="-9.999"]<-NA
N8W110_temp$air_temp[N8W110_temp$air_temp=="-9.99"]<-NA
N8W110_temp<-na.omit(N8W110_temp)
```

```{r,echo = FALSE}
# Remove unrelated rows
S8W110_air <- read.csv("TAO_T8S110W_M_AIRT_daily.ascii", sep=" ", header = FALSE)
S8W110_air <- S8W110_air[-c(1,2),-c(2,4:14)]
S8W110_sea <- read.csv("TAO_T8S110W_M_SST_daily.ascii", sep=" ", header = FALSE)
S8W110_sea <- S8W110_sea[-c(1,2),-c(4:14)]
S8W110_air.tidy <- S8W110_air %>% filter(V1 != "Height",V1!="YYYYMMDD", V1 != "Deployment:")
S8W110_sea.tidy <- S8W110_sea %>% filter(V1 != "Height",V1!="YYYYMMDD", V1 != "Deployment:", V1 != "Depth")
# Rename column names
colnames(S8W110_sea.tidy) <- c("date_time","time_diff","sea_temp")
colnames(S8W110_air.tidy) <- c("date_time","air_temp")
# Join to one data set
S8W110_air.tidy[,1]<-as.character(S8W110_air.tidy[,1])
S8W110_air.tidy[,2]<-as.character(S8W110_air.tidy[,2])
S8W110_sea.tidy[,1] <-as.character(S8W110_sea.tidy[,1])
S8W110_sea.tidy[,2] <-as.character(S8W110_sea.tidy[,2])
S8W110_sea.tidy[,3] <-as.character(S8W110_sea.tidy[,3])

S8W110_temp<-full_join(S8W110_sea.tidy,S8W110_air.tidy, by ="date_time", copy = FALSE)
# Add team_num, reading_type, time_diff, latitude, longtitude
S8W110_temp $team_num <-"14"
S8W110_temp $reading_type <-"buoy"
S8W110_temp $time_diff <-"0"
S8W110_temp $Lat <-"-8"
S8W110_temp $Lon <-"-110"
# Reorder the clumns
S8W110_temp<-S8W110_temp[,c('team_num','reading_type','time_diff','date_time','Lat','Lon','sea_temp','air_temp')]

# Add hours to date_time
S8W110_temp$date_time <- ymd(S8W110_temp$date_time)
hour(S8W110_temp$date_time) <- 12

# Change data type
S8W110_temp $team_num <-as.integer(S8W110_temp $team_num)
S8W110_temp $Lat <-as.numeric(S8W110_temp$Lat)
S8W110_temp $Lon <-as.numeric(S8W110_temp$Lon)
S8W110_temp$sea_temp <-as.numeric(S8W110_temp$sea_temp)
S8W110_temp$air_temp <-as.numeric(S8W110_temp$air_temp)

# Remove NAs
S8W110_temp$sea_temp[S8W110_temp$sea_temp=="-9.999"]<-NA
S8W110_temp$air_temp[S8W110_temp$air_temp=="-9.99"]<-NA
S8W110_temp<-na.omit(S8W110_temp)
```


## Summary of 5 buoys data
```{r results="asis", echo = FALSE}

sum1 <- data.table(Buoy=c("N0W155","S8E165","N8E165","N8W110","S8W110"), Minimum= c(min(N0W155_temp$sea_temp),min(S8E165_temp$sea_temp),min(N8E165_temp$sea_temp),min(N8W110_temp$sea_temp),min(S8W110_temp$sea_temp)), Median =c(median(N0W155_temp$sea_temp),median(S8E165_temp$sea_temp),median(N8E165_temp$sea_temp),median(N8W110_temp$sea_temp),median(S8W110_temp$sea_temp)), Average = c(mean(N0W155_temp$sea_temp),mean(S8E165_temp$sea_temp),mean(N8E165_temp$sea_temp),mean(N8W110_temp$sea_temp),mean(S8W110_temp$sea_temp)), Maximum = c(max(N0W155_temp$sea_temp),max(S8E165_temp$sea_temp),max(N8E165_temp$sea_temp),max(N8W110_temp$sea_temp),max(S8W110_temp$sea_temp)))
print(knitr::kable(sum1, caption = "Sea Surface Tempurature"))

sum2 <- data.table(Buoy=c("N0W155","S8E165","N8E165","N8W110","S8W110"), Minimum= c(min(N0W155_temp$air_temp),min(S8E165_temp$air_temp),min(N8E165_temp$air_temp),min(N8W110_temp$air_temp),min(S8W110_temp$air_temp)), Median =c(median(N0W155_temp$air_temp),median(S8E165_temp$air_temp),median(N8E165_temp$air_temp),median(N8W110_temp$air_temp),median(S8W110_temp$air_temp)), Average = c(mean(N0W155_temp$air_temp),mean(S8E165_temp$air_temp),mean(N8E165_temp$air_temp),mean(N8W110_temp$air_temp),mean(S8W110_temp$air_temp)), Maximum = c(max(N0W155_temp$air_temp),max(S8E165_temp$air_temp),max(N8E165_temp$air_temp),max(N8W110_temp$air_temp),max(S8W110_temp$air_temp)))
print(knitr::kable(sum2, caption = "Air Tempurature"))
```


##Buoy1: 0N155W
```{r, echo = FALSE}
#clean data
N0W155_temp$sea_temp<-as.numeric(N0W155_temp$sea_temp)
N0W155_temp$air_temp<-as.numeric(N0W155_temp$air_temp)

#calculate mean temperature of each year
N0W155_temp.plot <- N0W155_temp
N0W155_temp.plot$year<-year(N0W155_temp.plot$date_time)
sea<-data.frame(aggregate(N0W155_temp.plot$sea_temp~year, data=N0W155_temp.plot, mean))    
air<-data.frame(aggregate(N0W155_temp.plot$air_temp~year, data=N0W155_temp.plot, mean))
colnames(sea) <- c("year","sea_surface_temperature")
colnames(air) <- c("year","air_temperature")
#draw plot
#par(mfrow=c(1,2))
a <- ggplot(sea,mapping = aes(x =year, y=sea_surface_temperature))+geom_point() +
  geom_smooth(method = 'loess')
b <- ggplot(air,mapping = aes(x=year, y=air_temperature)) + geom_point() +
  geom_smooth(method = 'loess')

ggarrange(a,b)
```

## Buoy2: 8N165E
```{r, echo = FALSE}
#clean data
N8E165_temp$sea_temp<-as.numeric(N8E165_temp$sea_temp)
N8E165_temp$air_temp<-as.numeric(N8E165_temp$air_temp)

#calculate mean temperature of each year
N8E165_temp.plot <- N8E165_temp
N8E165_temp.plot$year<-year(N8E165_temp.plot$date_time)
sea<-data.frame(aggregate(N8E165_temp.plot$sea_temp~year, data=N8E165_temp.plot, mean))    
air<-data.frame(aggregate(N8E165_temp.plot$air_temp~year, data=N8E165_temp.plot, mean))
colnames(sea) <- c("year","sea_surface_temperature")
colnames(air) <- c("year","air_temperature")

#draw plot
a <- ggplot(sea,mapping = aes(x =year, y=sea_surface_temperature))+geom_point() +
  geom_smooth(method = 'loess')
b <- ggplot(air,mapping = aes(x=year, y=air_temperature)) + geom_point() +
  geom_smooth(method = 'loess')
ggarrange(a, b)

```

## Buoy3: 8S165E
```{r, echo = FALSE}
#clean data
S8E165_temp$sea_temp<-as.numeric(S8E165_temp$sea_temp)
S8E165_temp$air_temp<-as.numeric(S8E165_temp$air_temp)

#calculate mean temperature of each year
S8E165_temp.plot <- S8E165_temp
S8E165_temp.plot$year<-year(S8E165_temp.plot$date_time)
sea<-data.frame(aggregate(S8E165_temp.plot$sea_temp~year, data=S8E165_temp.plot, mean))    
air<-data.frame(aggregate(S8E165_temp.plot$air_temp~year, data=S8E165_temp.plot, mean))
colnames(sea) <- c("year","sea_surface_temperature")
colnames(air) <- c("year","air_temperature")

#draw plot
a <- ggplot(sea,mapping = aes(x =year, y=sea_surface_temperature))+geom_point() +
  geom_smooth(method = 'loess')
b <- ggplot(air,mapping = aes(x=year, y=air_temperature)) + geom_point() +
  geom_smooth(method = 'loess')
ggarrange(a, b)

```

## Buoy4: 8N110W
```{r, echo = FALSE}
#clean data
N8W110_temp$sea_temp<-as.numeric(N8W110_temp$sea_temp)
N8W110_temp$air_temp<-as.numeric(N8W110_temp$air_temp)

#calculate mean temperature of each year
N8W110_temp.plot <- N8W110_temp
N8W110_temp.plot$year<-year(N8W110_temp.plot$date_time)
sea<-data.frame(aggregate(N8W110_temp.plot$sea_temp~year, data=N8W110_temp.plot, mean))    
air<-data.frame(aggregate(N8W110_temp.plot$air_temp~year, data=N8W110_temp.plot, mean))
colnames(sea) <- c("year","sea_surface_temperature")
colnames(air) <- c("year","air_temperature")

#draw plot
a <- ggplot(sea,mapping = aes(x =year, y=sea_surface_temperature))+geom_point() +
  geom_smooth(method = 'loess')
b <- ggplot(air,mapping = aes(x=year, y=air_temperature)) + geom_point() +
  geom_smooth(method = 'loess')
ggarrange(a, b)
```

## Buoy5: 8S110W
```{r, echo = FALSE}
#clean data
S8W110_temp$sea_temp<-as.numeric(S8W110_temp$sea_temp)
S8W110_temp$air_temp<-as.numeric(S8W110_temp$air_temp)

#calculate mean temperature of each year
S8W110_temp.plot <- S8W110_temp
S8W110_temp.plot$year<-year(S8W110_temp.plot$date_time)
sea<-data.frame(aggregate(S8W110_temp.plot$sea_temp~year, data=S8W110_temp.plot, mean))    
air<-data.frame(aggregate(S8W110_temp.plot$air_temp~year, data=S8W110_temp.plot, mean))
colnames(sea) <- c("year","sea_surface_temperature")
colnames(air) <- c("year","air_temperature")

#draw plot
a <- ggplot(sea,mapping = aes(x =year, y=sea_surface_temperature))+geom_point() +
  geom_smooth(method = 'loess')
b <- ggplot(air,mapping = aes(x=year, y=air_temperature)) + geom_point() +
  geom_smooth(method = 'loess')
ggarrange(a, b)
```

##Data Sources
###1) 0N155W
####Air Temperature
http://tao.ndbc.noaa.gov/tao/data_download/cache/201711/06-6688/TAO_T0N155W_M_AIRT_daily.ascii

####Sea Temperature
http://tao.ndbc.noaa.gov/tao/data_download/cache/201711/d06-350/TAO_T0N155W_M_SST_daily.ascii

###2) 8S165E
####Air Temperature
http://tao.ndbc.noaa.gov/tao/data_download/cache/201711/06-6688/TAO_T8S165E_M_AIRT_daily.ascii

####Sea Temperature
http://tao.ndbc.noaa.gov/tao/data_download/cache/201711/d06-350/TAO_T8S165E_M_SST_daily.ascii

###3) 8N165E
####Air Temperature
http://tao.ndbc.noaa.gov/tao/data_download/cache/201711/06-6688/TAO_T8N165E_M_AIRT_daily.ascii

####Sea Temperature
http://tao.ndbc.noaa.gov/tao/data_download/cache/201711/d06-350/TAO_T8N165E_M_SST_daily.ascii

###4) 8S110W
####Air Temperature
http://tao.ndbc.noaa.gov/tao/data_download/cache/201711/06-6688/TAO_T8S110W_M_AIRT_daily.ascii

####Sea Temperature
http://tao.ndbc.noaa.gov/tao/data_download/cache/201711/d06-350/TAO_T8S110W_M_SST_daily.ascii

###5) 8N110W
####Air Temperature:
http://tao.ndbc.noaa.gov/tao/data_download/cache/201711/06-6688/TAO_T8N110W_M_AIRT_daily.ascii

####Sea Temperature:
http://tao.ndbc.noaa.gov/tao/data_download/cache/201711/d06-350/TAO_T8N110W_M_SST_daily.ascii
